
{\color{red}What have you learned from these results?  What are the next steps? These questions should be answered here, or better yet, in a new Conclusions chapter.}

\section{What have we learned (find better name for this)}


\section{Next Steps }


\section{Remaining Milestones}
The two remaining milestones serve as goalposts for the second half of the CGU Math Clinic year:
\begin{itemize}
\item Determine the importance of different crack features for the prediction of the evolution of the fracture network.
\item Refine and add complexity to the network (i.e.,\ additional convolutional filters, layered graph convolution, compare effectiveness of spectral clustering graph convolutions versus standard graph convolutions).
\end{itemize}



\section{Deliverable Status}
\begin{enumerate}
\item Keras implementation of proposed architecture, coded in Python.
	\begin{itemize}
		\item In progress.
	\end{itemize} 
\item Full documentation of code in iPython Notebook.
	\begin{itemize}
		\item In progress. On track to be finalized along with final code.
	\end{itemize} 
\item Midterm presentation.
	\begin{itemize}
		\item Complete, November 14, 2017.
	\end{itemize} 
\item Mid-year report.
	\begin{itemize}
		\item Complete, December 18, 2017.
	\end{itemize} 
\item Journal article on the dynamic prediction of the fracture of brittle material using deep learning, submitted to peer-reviewed journal.
	\begin{itemize}
		\item Forthcoming, Spring 2018.
	\end{itemize} 
\item Final presentation.
	\begin{itemize}
		\item Forthcoming, Spring 2018.
	\end{itemize} 
\item Final report.
	\begin{itemize}
		\item Forthcoming, Spring 2018.
	\end{itemize} 
\end{enumerate}